Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-06-13 main.tex
Started improving discussion.

\section{Results}
%
The coefficient estimates for a single-level logistic regression at
6~\unit{\kph} with gain $g=10$ are shown in
Table~\ref{table:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors. Larger
angular impulse increases the probability to fall and enduring more
perturbations or having the balance assist on, decrease the probability to
fall.  The associated multiplicative change in odds are shown in
Table~\ref{table:freq-coefs-6}.

\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    6~\unit{\kilo\meter\per\hour} and gain $g=10$. Multiplicative change in
    odds of predictor variables at 6 \unit{\kilo\meter\per\hour} and gain
    $g=10$ based on frequentist single-level logistic regression.}
  \label{table:freq-coefs-6}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & Estimate & Standard error & \(p\)-value & MCiO & 2.5\% & 97.5\% \\
    \midrule
    Intercept & -0.29 & 0.17 & 0.09 & 0.75 & 0.53 & 1.05 \\
    Angular impulse & 1.69 & 0.27 & 0.00 & 5.40 & 3.18 & 9.16 \\
    Perturbation order & -0.77 & 0.22 & 0.00 & 0.46 & 0.30 & 0.72 \\
    Balance assist state & -0.64 & 0.27 & 0.02 & 0.53 & 0.31 & 0.89 \\
    Roll angle & -0.25 & 0.21 & 0.24 & 0.78 & 0.51 & 1.18 \\
    Steer angle & -0.14 & 0.21 & 0.51 & 0.87 & 0.58 & 1.32 \\
    Balance-assist on $\times$ roll angle & 0.52 & 0.34 & 0.12 & 1.68 & 0.86 & 3.29 \\
    Balance-assist on $\times$ steer angle & -0.41 & 0.34 & 0.22 & 0.66 & 0.34 & 1.28 \\
    Balance-assist on $\times$ angular impulse & 0.41 & 0.41 & 0.32 & 1.51 & 0.67 & 3.38 \\
    Balance-assist on $\times$ perturbation order & -0.53 & 0.34 & 0.12 & 0.59 & 0.30 & 1.15 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\section{Discussion}

\subsection{Balance-assist}

Turning the balance-assist system on significantly \((p<0.05)\) reduces the
odds that a fall occurs while cycling at a speed of 1.7~\si{\mps} but at
2.8~\si{\mps} that is not the case \((p=0.07)\). If all other factors remain
the same at 1.7~\si{\mps}, the balance-assist system halves the odds that a
perturbation results in a fall. How much this changes the probability that a
fall occurs depends on the values of the other predictor variables: if the odds
that a perturbation results in a fall are a 1000:1, turning on the
balance-assist system reduces the odds to 500:1. However, the probability that
a fall occurs is only reduced from $0.999$ to $0.998$. On the other hand, if
the odds that a fall will occur are smaller, halving the odds has a larger
influence on the fall probability. For example, if the odds that a fall occurs
is two, halving it to one reduces the probability from $0.66$ to $0.50$. Figure
\ref{fig:probability} shows how the balance-assist system changes the fall
probability for different magnitudes of angular impulse.

\begin{figure}
  \centering
  \subcaptionbox{1.7~\si{\mps}}{
    \includegraphics[width=70mm]{example-image-a}
  }
  \subcaptionbox{2.8~\si{\mps}}{
    \includegraphics[width=70mm]{example-image-b}
  }
  \caption{Comparison of predicted fall probability for balance-assist on or
    off All other predictor variables are fixed at zero, except for the
    interaction effect between the balance-assist and the angular impulse.}
  \label{fig:probability}
\end{figure}

>>>>

\section{Results}
%
The coefficient estimates for a single-level logistic regression at
6~\unit{\kph} with gain $g=10$ are shown in
Table~\ref{table:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors. Larger
angular impulse increases the probability to fall and enduring more
perturbations or having the balance assist on, decrease the probability to
fall.  The associated multiplicative change in odds are shown in
Table~\ref{table:freq-coefs-6}.
%
\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates at
    6~\unit{\kilo\meter\per\hour} and gain $g=10$. Multiplicative change in
    odds of predictor variables at 6 \unit{\kilo\meter\per\hour} and gain
    $g=10$ based on frequentist single-level logistic regression.}
  \label{table:freq-coefs-6}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & Estimate & Standard error & \(p\)-value & MCiO & 2.5\% & 97.5\% \\
    \midrule
    Intercept & -0.29 & 0.17 & 0.09 & 0.75 & 0.53 & 1.05 \\
    Angular impulse & 1.69 & 0.27 & 0.00 & 5.40 & 3.18 & 9.16 \\
    Perturbation order & -0.77 & 0.22 & 0.00 & 0.46 & 0.30 & 0.72 \\
    Balance assist state & -0.64 & 0.27 & 0.02 & 0.53 & 0.31 & 0.89 \\
    Roll angle & -0.25 & 0.21 & 0.24 & 0.78 & 0.51 & 1.18 \\
    Steer angle & -0.14 & 0.21 & 0.51 & 0.87 & 0.58 & 1.32 \\
    Balance-assist on $\times$ roll angle & 0.52 & 0.34 & 0.12 & 1.68 & 0.86 & 3.29 \\
    Balance-assist on $\times$ steer angle & -0.41 & 0.34 & 0.22 & 0.66 & 0.34 & 1.28 \\
    Balance-assist on $\times$ angular impulse & 0.41 & 0.41 & 0.32 & 1.51 & 0.67 & 3.38 \\
    Balance-assist on $\times$ perturbation order & -0.53 & 0.34 & 0.12 & 0.59 & 0.30 & 1.15 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\section{Discussion}
%
Turning the balance-assist system on significantly \((p<0.05)\) reduces the
odds that a fall occurs while cycling at a speed of 6~\si{\kph}.
Figure~\ref{fig:probability-6kph} visualizes the probability of falling as a
function of the angular impulse while keeping all other explantory factors at
their mean values. This figure is derived from the result that the
balance-assist system halves the odds that a perturbation results in a fall.
This figure shows that for relatively large impulses the probability to fall is
unity for both states of balance assist on and off. And for relatively small
impulses the probability to fall is zero for both states. But for impulses in
the magnitude region around the mean fall threshold, the probability of falling
is significantly lowered.

but at
10~\si{\kph} that is not the case \((p=0.07)\).  How much this changes the probability that a
fall occurs depends on the values of the other predictor variables: if the odds
that a perturbation results in a fall are a 1000:1, turning on the
balance-assist system reduces the odds to 500:1. However, the probability that
a fall occurs is only reduced from $0.999$ to $0.998$. On the other hand, if
the odds that a fall will occur are smaller, halving the odds has a larger
influence on the fall probability. For example, if the odds that a fall occurs
is two, halving it to one reduces the probability from $0.66$ to $0.50$. Figure
\ref{fig:probability} shows how the balance-assist system changes the fall
probability for different magnitudes of angular impulse.

\begin{figure}
  \centering
  \subcaptionbox{1.7~\si{\mps}\label{fig:probability-6kph}}{
    \includegraphics[width=120mm]{figures/predicted_fall_probability_6kmh.png}
  }
  \subcaptionbox{2.8~\si{\mps}}{
    \includegraphics[width=120mm]{figures/predicted_fall_probability_10kmh.png}
  }
  \caption{Comparison of predicted fall probability for balance-assist on or
    off All other predictor variables are fixed at zero, except for the
    interaction effect between the balance-assist and the angular impulse.}
  \label{fig:probability}
\end{figure}
